---
title: "Strawberries"
author: Carolyn Wright, Rachel Donahue, Ranfei Xu, Zara Waheed
date: November 3rd, 2021
output: revealjs::revealjs_presentation
theme: white
---

# Research Question:
<div style="font-size:40pt">


- How has **toxic chemical** usage changed over **time** 
- and does this vary across different **states**?


```{r, include=FALSE} 
source(file = "Wrangling.R", echo = FALSE)
source(file = "Plots.R", echo = FALSE)
library(plotly)
```

# Investigate overall toxin instances
<div style="font-size:16pt">


```{r, echo=FALSE, warning=FALSE}
p<-ggplot(CHEMICALS_MEASURED_IN_LB_CAR_COUNTS_HIST, mapping = aes(x = name, y = value, fill = name)) +geom_bar(stat="identity") +
  ggtitle("Overall Toxin Counts") + xlab("Toxin") + ylab("Pounds") +  scale_fill_brewer(palette = "Reds") +
  theme(panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(angle = 45, vjust=.6),
        legend.position="none"

  )

ggplotly(p, tooltip="y")     

```

# Distribution of Carcinogens

```{r, include=FALSE} 
#Code not to be displayed here
```
```{r, echo=FALSE, warning=FALSE}
#code for graphs here
Carcinogen_usmap
```


# Especially in California

- California had 11 main Carcinogenic chemicals detected in strawberry yields.
- They fall into the known, possible and probable categories. 
- The figure below shows a scaled plot of the distribution of Carcinogens detected in strawberries in California over time.

# Total Carcinogens CA

```{r, echo=FALSE, warning=FALSE}
p2<-ggplot(subset(Chem_Car_Group1, State == "CALIFORNIA"), mapping = aes(x = Year, y = Total_Carcinogen, color = Carcinogen )) + 
  geom_point() +ylab("Pounds")+ xlim(1990, 2020) + ylim(0, 300000) + scale_color_manual(breaks = c("known","possible","probable"), values = c("firebrick","lightpink2","mistyrose3")) 

ggplotly(p2, tooltip="y")
```



# Known carcinogenic chemicals 

```{r, echo=FALSE, warning=FALSE}
#code for graphs here
ggplotly(California_Plots("known"), tooltip="y")
```

# Probable carcinogenic chemicals 
```{r, include=FALSE} 
plot_probable <- ggplot(subset(Carcinogens, State == "CALIFORNIA" & Carcinogen == "probable"), mapping = aes(x = Year, y = Value1, color = Chemical )) +
  geom_point(shape=25, size=2, stroke = 1) + ggtitle(paste0("CA - ","probable"," carcinogen")) + xlim(1990, 2020) + ylab("Pounds") +
  scale_color_brewer(palette = "RdGy") +
  theme(panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(face = "bold", size = (8)), 
        legend.title = element_text(face = "bold", size =(8)), 
        legend.text = element_text(size =(8)), 
        axis.title = element_text( size = (8)),
        axis.text = element_text(size = (8)))

```
```{r, echo=FALSE, warning=FALSE}
#code for graphs here
ggplotly(plot_probable, tooltip="y")
```

# Possible carcinogenic chemicals

```{r, include=FALSE} 
plot_possible <- ggplot(subset(Carcinogens, State == "CALIFORNIA" & Carcinogen == "possible"), mapping = aes(x = Year, y = Value1, color = Chemical )) +
  geom_point(shape=25, size=2, stroke = 1) + ggtitle(paste0("CA - ","possible"," carcinogen")) + xlim(1990, 2020) + ylab("Pounds") +
  scale_color_brewer(palette = "RdGy") +
  theme(panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        plot.title = element_text(face = "bold", size = (8)), 
        legend.title = element_text(face = "bold", size =(8)), 
        legend.text = element_text(size =(8)), 
        axis.title = element_text( size = (8)),
        axis.text = element_text(size = (8)))

```
```{r, echo=FALSE, warning=FALSE}
#code for graphs here
plot_possible
```

# Thoughts


<div style="font-size:30px">


**Trends on the known toxins**


<span style="color:green">
 Captan, Carbaryl and Iprodione  
</span> 
 

**Related policy**


<span style="color:green">
California Office of Environmental Health Hazard Assessment (OEHNA) -- Proposition 65  
</span> 


**Further steps**


<span style="color:green">
  Why Captan is still used as widely as it is if it is toxic?
</span> 

